%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\begin{cventries}
  \cventry
    {Peer Reviewer} % Affiliation/role
    {PLOS ONE} % Organization/group
    {San Francisco, CA} % Location
    {Feb. 2018 -present} % Date(s)
    {}
    {}
\end{cventries}
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {Peer Reviewer} % Affiliation/role
    {International Journal of Radiation Oncology * Biology * Physics} % Organization/group
    {Arlington, VA} % Location
    {Jan. 2018 -present} % Date(s)
    {}
    {}
\end{cventries}
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {Judge} % Affiliation/role
    {LSU Undergraduate Research Conference} % Organization/group
    {Baton Rouge, LA} % Location
    {Nov. 17, 2017} % Date(s)
    {}
    {}
\end{cventries}
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {Volunteer Crisis Intervention Specialist} % Affiliation/role
    {Crisis Intervention Center} % Organization/group
    {Baton Rouge, LA} % Location
    {Sep. 2017 - present} % Date(s)
    {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Completed rigorous training (70+ hours) to become volunteer crisis intervention specialist counselor for crisis intervention and suicide prevention}
      \item {For more information about the Crisis Intervention Center, visit: \url{https://cicla.org/}}
    \end{cvitems}
    }
    {}
\end{cventries}
%
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {Guest Member} % Affiliation/role
    {New Professionals Subcommittee \& Professional Mentorship Working Group} % Organization/group
    {Alexandria, VA} % Location
    {Jun. 2017 - present} % Date(s)
    {}
    {American Association of Physicists in Medicine}
\end{cventries}
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {Volunteer} % Affiliation/role
    {LSU Discover Day} % Organization/group
    {Baton Rouge, LA} % Location
    {Apr. 4, 2017} % Date(s)
    {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Registered participating students and judges for university-wide undergraduate research symposium}
    \end{cvitems}
    }
    {}
\end{cventries}
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {Department of Physics \& Astronomy} % Affiliation/role
    {Private Tutor} % Organization/group
    {Baton Rouge, LA} % Location
    {Jan. 2017 - present} % Date(s)
    {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Tutor local high school and undergraduate students in introductory physics and mathematics courses}
      \item {5-star tutor rating via Tutor Matching Service: \url{https://tutormatchingservice.com/#/tutor/4488}}
    \end{cvitems}
    }
    {}
\end{cventries}
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {President/Member} % Affiliation/role
    {American Nuclear Society - LSU Student Chapter} % Organization/group
    {Baton Rouge, LA} % Location
    {Aug. 2016 - present} % Date(s)
    {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Led Girl Scout Get to Know Nuclear Worshop; led activity teaching local Girl Scout troops about radioactivity and half-life by oberving the 'half-life' of pennies}
      \item {Led Boy Scout Merit Badge Workshop; led an electroscope activity for Boy Scouts at the Riverbend Nuclear Power Plant}
    \end{cvitems}
    }
    {}
\end{cventries}
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {Program/Medical Assistant} % Affiliation/role
    {LSU Medical Physics \& Health Physics Graduate Program} % Organization/group
    {Baton Rouge, LA} % Location
    {Jan. 2016 - May 2016} % Date(s)
    {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Led organization and preparation for multiple outreach evens and program promotion projects}
      \item {Manned program booths at LSU Career Expo and LSU Graduate Studies Fair}
      \item {Created informational brochures for all degree tracks (4) in the program}
      \item {Served as student liason for prospective program applicants}
      \item {Led planning and organization of social events for applicant interview weekend}
      \item {Assisted in compilation and editing of student-led program audit}
      \item {Assisted program director with CAMPEP re-accreditation process}
    \end{cvitems}
    }
    {}
\end{cventries}
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {Teaching Assistant} % Affiliation/role
    {LSU Department of Physics \& Astronomy} % Organization/group
    {Baton Rouge, LA} % Location
    {Aug. 2014 - Aug. 2015} % Date(s)
    {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Instructed two sections each semester (totaling 150+ students) of general physics II laboratory (PHYS 2109)}
      \item {Prepared weekly lectures covering topics in electricty, magnetism, and optics, among others}
      \item {Graded weekly lab reports; wrote and graded final exam}
      \item {Tutored physics for undergraduates in Nicholson Tutoring Center 5 hours every week}
      \item {Proctored mid-semester and final exam for introductory phyiscs courses}
    \end{cvitems}
    }
    {}
\end{cventries}
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {President (2013-14)/Secretary (2012-13)/Memeber} % Affiliation/role
    {Davidson College Society of Physics Students} % Organization/group
    {Davidson, NC} % Location
    {Aug. 2011 - May 2014} % Date(s)
    {}
    {}
\end{cventries}
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {Officer (2013-14)/Member} % Affiliation/role
    {Davidson College Bernard Society of Mathematics} % Organization/group
    {Davidson, NC} % Location
    {Aug. 2012 - May 2014} % Date(s)
    {}
    {}
\end{cventries}
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {Physics and Math Tutor} % Affiliation/role
    {Davidson College Math and Science Center} % Organization/group
    {Davidson, NC} % Location
    {Aug. 2011 - May 2014} % Date(s)
    {}
    {}
\end{cventries}
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {Homework Grader} % Affiliation/role
    {Davidson College Mathematics Department} % Organization/group
    {Davidson, NC} % Location
    {Aug. 2010 - May 2012} % Date(s)
    {}
    {}
\end{cventries}
%---------------------------------------------------------
\begin{cventries}
  \cventry
    {Tutor} % Affiliation/role
    {Ada Jenkins Center} % Organization/group
    {Davidson, NC} % Location
    {Aug. 2010 - May 2011} % Date(s)
    {}
    {LEARN Works Program}
\end{cventries}
%---------------------------------------------------------
